\LARGE \bf Steering a Swarm Using Global Inputs And Swarm Statistics

### 2016-08-09 journalSwarmControl/Introduction.tex
Added sections for funding and for conclusion and for the algorithm
fixed the algorithm
updated MDP and policy iteration, did all captions, added new pic, removed extra images
added images for foraging

\begin{figure}
\renewcommand{\figwid}{0.32\columnwidth}
\subfloat[][Vary Number]{\label{fig:VaryNum}
\begin{overpic}[width =\figwid]{VaryNum.pdf}\end{overpic}}
%
\subfloat[][Vary Visual Feedback]{\label{fig:VaryVis}
\begin{overpic}[width =\figwid]{VaryVisFS.pdf}\end{overpic}
\begin{overpic}[width =\figwid]{VaryVisMV.pdf}\end{overpic}}\\
%
\subfloat[][Vary Control]{\label{fig:VaryControl}
\begin{overpic}[width =\figwid]{VaryControl.pdf}\end{overpic}}
%
\subfloat[][Vary Noise]{\label{fig:VaryNoise}
\begin{overpic}[width =\figwid]{VaryNoise.pdf}\end{overpic}}
%
\subfloat[][Control Position]{\label{fig:ControlPos}
\begin{overpic}[width =\figwid]{ControlPos.pdf}\end{overpic}}
%
\caption{\label{fig:5experiments}
Screenshots from our five online experiments controlling multi-robot systems with limited, global control.
\textbf{(a)} Varying the number of robots from 1-500
\textbf{(b)} Comparing 4 levels of visual feedback 
\textbf{(c)} Comparing 3 control architectures
\textbf{(d)} Varying noise from 0 to 200\% of control authority
\textbf{(e)} Controlling the position of 1 to 10 robots.
\href{http://youtu.be/HgNENj3hvEg}{See video overview at \cite{ShivaVideo2015}}
\vspace{-2em}
}
\end{figure}

Our goal was to test several scenarios involving large-scale human-swarm interaction (HSI), and to do so with a statistically-significant sample size. Towards this end, we created \href{http://www.swarmcontrol.net/show_results}{SwarmControl.net}, an open-source online testing platform suitable for inexpensive deployment and data collection on a scale not yet seen in swarm robotics research. Screenshots from this platform are shown in Fig.~\ref{fig:5experiments}.  \href{https://github.com/crertel/swarmmanipulate.git}{All code} \href{http://www.swarmcontrol.net/show_results}{and experimental results} are posted online, \cite{Chris-Ertel2013}. {TODO: link to 2016 code}

@@

\begin{figure}
\centering
\begin{overpic}[width=0.5\columnwidth]{CompleteMazeDescription.pdf}\end{overpic}
\begin{overpic}[width=0.438\columnwidth]{MainExpFig.pdf}\end{overpic}
%\todo{I like the 'target' symbol, but it is not self-documenting.  We need a legend explaining the min and max variance ellipses, the goal region, the variance, the mean, the object COM, and the target mean position.  I think these are easiest to make in powerpoint.
%Please use the same color and line style for the variance min and max as you use in Figure 4.
%}
%{blockpushingImageWithMeanAndVarianceOverlay.png}
\caption{\label{fig:bigPictureMeanAndVarianceForSwarm} A swarm of robots, all controlled by a uniform force field, can be effectively controlled by a hybrid controller that knows only the first and second moments of the robot distribution.  Here a swarm of simple robots (blue discs) pushes a green hexagon toward the goal. See video attachment~\cite{ShivaVideo2015}.}
\end{figure}
 %function and implementation function

>>>>

\begin{figure}
\renewcommand{\figwid}{0.32\columnwidth}
\subfloat[][Vary Number]{\label{fig:VaryNum}
\begin{overpic}[width =\figwid]{VaryNum.pdf}\end{overpic}}
%
\subfloat[][Vary Visual Feedback]{\label{fig:VaryVis}
%\begin{overpic}[width =\figwid]{VaryVisFS.pdf}\end{overpic}
\begin{overpic}[width =\figwid]{VaryVisCH.pdf}\end{overpic}}
%
\subfloat[][Vary Noise]{\label{fig:VaryNoise}
\begin{overpic}[width =\figwid]{VaryNoise.pdf}\end{overpic}}\\
%
\subfloat[][Control Position]{\label{fig:ControlPos}
\begin{overpic}[width =\figwid]{ControlPos.pdf}\end{overpic}}
%
\subfloat[][Vary Control: Assembly]{\label{fig:VaryControl}
\begin{overpic}[width =\figwid]{VaryControl.pdf}\end{overpic}}
%
\subfloat[][Cary Control: Foraging]{\label{fig:Forage}
\begin{overpic}[width =\figwid]{VaryForage.pdf}\end{overpic}}
%
\caption{\label{fig:5experiments}
Screenshots from our online experiments controlling multi-robot systems with limited, global control.
\textbf{(a)} Varying the number of robots from 1-500
\textbf{(b)} Comparing 4 levels of visual feedback 
\textbf{(c)} Varying noise from 0 to 200\% of control authority
\textbf{(d)} Controlling the position of 1 to 10 robots
\textbf{(e)} Comparing 3 control architectures to assemble
\textbf{(f)} Comparing 3 control architectures to forage.
\vspace{-2em}
}
\end{figure}

Our goal was to test several scenarios involving large-scale human-swarm interaction (HSI), and to do so with a statistically-significant sample size. Towards this end, we created \href{http://www.swarmcontrol.net/show_results}{SwarmControl.net}, an open-source online testing platform suitable for inexpensive deployment and data collection on a scale not yet seen in swarm robotics research. Screenshots from this platform are shown in Fig.~\ref{fig:5experiments}.  \href{https://github.com/crertel/swarmmanipulate.git}{All code} \href{http://www.swarmcontrol.net/show_results}{and experimental results} are posted online, \cite{Chris-Ertel2013}. \todo{TODO: Chris, is 2016 code ready to upload? link to 2016 code}

@@

\begin{figure}
\centering
\begin{overpic}[width=0.5\columnwidth]{CompleteMazeDescription.pdf}\end{overpic}
\begin{overpic}[width=0.438\columnwidth]{MainExpFig.pdf}\end{overpic}
%\todo{I like the 'target' symbol, but it is not self-documenting.  We need a legend explaining the min and max variance ellipses, the goal region, the variance, the mean, the object COM, and the target mean position.  I think these are easiest to make in powerpoint.
%Please use the same color and line style for the variance min and max as you use in Figure 4.
%}
%{blockpushingImageWithMeanAndVarianceOverlay.png}
\caption{\label{fig:bigPictureMeanAndVarianceForSwarm} A swarm of robots, all controlled by a uniform force field, can be effectively controlled by a hybrid controller that knows only the first and second moments of the robot distribution.  Here a swarm of simple robots (blue discs) pushes a green hexagon toward the goal. Simulation at left, screen capture form hardware experiment at right. See video attachment~\cite{ShivaVideo2015}.}
\end{figure}
 %function and implementation function

### 2016-08-09 journalSwarmControl/expResults.tex
added images for foraging

We designed five experiments to investigate human control of large robotic swarms for manipulation tasks.  Screenshots of each experiment are shown in Fig.~\ref{fig:5experiments}.  Each experiment examined the effects of varying a single parameter: population of robots for manipulation, four levels of visual feedback, three control architectures, different levels of Brownian noise, and position control with 1 to 10 robots. The users could choose which experiment to try, and then our architecture randomly assigned a particular parameter value for each trial.  We recorded the completion time and the participant ID for each successful trial.  
%As Fig.~\ref{fig:Learning} shows, one-third of all participants played only a single game.  Still, many played multiple games, and their decreasing completion times demonstrates their skills improved.

@@

\paragraph{Varying control}
Ultimately, we want to use swarms of robots to build things. This experiment compared different control architectures modeled after real-world devices.

The results were conclusive, as shown in Fig.~\ref{fig:ResVaryControlVis}.a: attractive control was the fastest, followed by global control, with repulsive control a distant last.  The median time using repulsive control was four times longer than with attractive control.
Using ANOVA analysis, we reject the null hypothesis that all controllers are equivalent, with $p$-value $3.37\times10^{-32}$.

\begin{figure}[b!]
\renewcommand{\figwid}{0.5\columnwidth}
\begin{overpic}[width =\figwid]{ResVaryControl.pdf}\end{overpic}
\begin{overpic}[width =\figwid]{ResVaryVis.pdf}\end{overpic}
\vspace{-1em}
\caption{\label{fig:ResVaryControlVis} Left: Attractive control resulted in the shortest completion time and repulsive the longest for building a three-block pyramid. Right: Completion-time results for the four levels of visual feedback shown in Fig.~\ref{fig:Visualization}.  Players performed better with limited feedback.
%\vspace{-1em}
}
\end{figure}

@@

@@

Our experiment indicated the opposite: players with just the mean completed the task faster than those with full-state feedback.  As Fig.~\ref{fig:ResVaryControlVis}.b shows, the levels of feedback arranged by increasing completion time are [mean + variance, mean, full-state, convex-hull].  All experiments lasting over 300s were removed, under the assumption that the user stopped playing
Using ANOVA analysis, we reject the null hypothesis that all visualization methods are equivalent, with $p$-value $2.69\times10^{-19}$.
Anecdotal evidence from beta-testers who played the game suggests that tracking 100 robots is overwhelming---similar to schooling phenomenons that confuse predators---while working with just the mean + variance is like using a ``spongy'' manipulator. Our beta-testers found convex-hull feedback confusing and irritating.  A single robot left behind an obstacle will stretch the entire hull, obscuring the majority of the swarm.
%obscuring what the rest of the swarm is doing.

@@

>>>>

We designed six experiments to investigate human control of large robotic swarms for manipulation tasks.  Screenshots of each experiment are shown in Fig.~\ref{fig:5experiments}.  Each experiment examined the effects of varying a single parameter: population of robots for manipulation, four levels of visual feedback, different levels of Brownian noise, position control with 1 to 10 robots, and three control architectures for both an assembly task and a foraging task. The users could choose which experiment to try, and then our architecture randomly assigned a particular parameter value for each trial.  We recorded the completion time and the participant ID for each successful trial.  
%As Fig.~\ref{fig:Learning} shows, one-third of all participants played only a single game.  Still, many played multiple games, and their decreasing completion times demonstrates their skills improved.

@@

@@

\begin{figure}[b!]
\renewcommand{\figwid}{0.5\columnwidth}
\begin{overpic}[width =\figwid]{ResVaryVis.pdf}\end{overpic}
\vspace{-1em}
\caption{\label{fig:ResVaryVis} Completion-time results for the four levels of visual feedback shown in Fig.~\ref{fig:Visualization}.  Players performed better with limited feedback.
%\vspace{-1em}
}
\end{figure}

@@

Our experiment indicated the opposite: players with just the mean completed the task faster than those with full-state feedback.  As Fig.~\ref{fig:ResVaryVis}.b shows, the levels of feedback arranged by increasing completion time are [mean + variance, mean, full-state, convex-hull].  All experiments lasting over 300s were removed, under the assumption that the user stopped playing
Using ANOVA analysis, we reject the null hypothesis that all visualization methods are equivalent, with $p$-value $2.69\times10^{-19}$.
Anecdotal evidence from beta-testers who played the game suggests that tracking 100 robots is overwhelming---similar to schooling phenomenons that confuse predators---while working with just the mean + variance is like using a ``spongy'' manipulator. Our beta-testers found convex-hull feedback confusing and irritating.  A single robot left behind an obstacle will stretch the entire hull, obscuring the majority of the swarm.
%obscuring what the rest of the swarm is doing.

@@

\paragraph{Varying control: Assembly}
Ultimately, we want to use swarms of robots to build things. This experiment compared different control architectures modeled after real-world devices.

The results were conclusive, as shown in Fig.~\ref{fig:ResVaryControl}.a: attractive control was the fastest, followed by global control, with repulsive control a distant last.  The median time using repulsive control was four times longer than with attractive control.
Using ANOVA analysis, we reject the null hypothesis that all controllers are equivalent, with $p$-value $3.37\times10^{-32}$.

\begin{figure}[b!]
\renewcommand{\figwid}{3.3cm}
\begin{overpic}[height =\figwid]{ResVaryControl.pdf}\end{overpic}
\begin{overpic}[height =\figwid]{ResVaryForage.pdf}\end{overpic}
\vspace{-.5em}
\caption{\label{fig:ResVaryControl} Completion time depends on both the task and the control type. Left: Attractive control resulted in the shortest completion time and repulsive the longest for building a three-block pyramid. Right: in the foraging test, global control resulted in the shortest completion time and attractive the longest.
%\vspace{-1em}
}
\end{figure}

\paragraph{Varying control: Foraging}
Collecting and delivering resources is necessary for drug delivery.
This experiment also compared attractive and repulsive control with the global control used for the other experiments. The experiment challenged players to collect particles using a swarm of 100 robots and return the particles to a home region. The robots encapsulate the particles on contact.

The results were conclusive, as shown in Fig.~\ref{fig:ResVaryControl}.b: global control was the fastest, followed by repulsive control, with attractive control last.  Using ANOVA analysis, we reject the null hypothesis that all controllers are equivalent, with $p$-value $2.96\times10^{-6}$.
